This is an example of article title

### 2025-10-28 paper/paper.tex
Further work on section 4.

\begin{figure}
    \centering
    \includegraphics[width=0.17\textwidth]{logo.png}
    \caption*{\ \\[-.5\baselineskip]Logo of \texttt{LieGroups.jl}.}%
    \label{fig:liegroups_logo}
\end{figure}

@@

\subsection{Lie groups}
We denote a Lie group by \(\mathcal{G} = (\mathcal{M}, \cdot)\) where \(\mathcal{M}\) is a smooth manifold and \(\cdot\) is the group operation.
A smooth manifold \(\mathcal{M}\) is a topological space that is locally isomorphic to an Euclidean space \(\mathbb{R}^n\) for some \(n \in \mathbb{N}\), but globally may have a different topology.
We call \(n\) the dimension of the manifold \(\mathcal{M}\), denoted by \(\dim(\mathcal{M}) = n\).
As an example, take the \(2\)-dimensional sphere
\begin{equation*}
\mathbb{S}^2 = \{x \in \mathbb{R}^3 \mid \lVert x\rVert = 1\},
\end{equation*}

@@

\subsubsection*{exponential and logarithm.}
An important tool to “move around” on the Lie group is the exponential map.\\
The (Lie group) exponential function \(\exp\colon \mathfrak{g} \to \mathcal{G}\) maps elements from the Lie algebra to the Lie group, and is formally defined \cite[Def.~9.2.2]{HilgertNeeb:2012} by evaluating the unique curve \(\gamma\colon \mathbb{R} \to \mathcal{G}\) that fulfils the differential equation
\begin{equation*}
\gamma'(t) = D\lambda_{\gamma(t)}(e)[X]
\quad\text{ with }\quad\gamma(0) = e \text{ and }\gamma'(0) = X
\end{equation*}
at time $t=1$, i.e.\ \(\exp(X) = \gamma(1)\).

@@

The inner product and norm on the Lie algebra are available as \verb|inner(|$\frak g$\verb|, X, Y)| and \verb|norm(|$\frak g$\verb|, X)|, respectively.
furthermore, there are two functions to convert between a coordinate-free representation of $X$ as a tangent vector and its representation in coordinates of a basis.

Given a vector $c \in \mathbb R^n$, we obtain the tangent vector by calling \verb|get_vector(|$\frak g$\verb|, c, B)| where $B$ is a basis of the tangent space, i.e.\ a subtype of \verb|AbstractBasis| and defaults within \verb|LieGroups.jl| to \verb|DefaultLieAlgebraOrthogonalBasis()|.
When a Lie group has different representations of points and tangent vectors, these are distinguished by calling \verb|get_vector(|$\frak g$\verb|, c, B, T)| specifying the tangent vector type.\footnote{in-place variant \texttt{get\_vector!($\frak g$, X::T, c, B)} contains the type information directly.}
Given a tangent vector $X \in \frak g$, we obtain its coordinates by calling \verb|get_coordinates(|$\frak g$\verb|, X, B)|\footnote{in-place variant \texttt{get\_coordinates!($\frak g$, c, X, B)}}, where the Basis is again optional.

@@

\subsubsection*{Jacobians.}
On Euclidean space, the terms differential and Jacobian are often used interchangeably.
On manifolds, the differential of a smooth map between two manifolds is a map between the corresponding tangent spaces. To represent this map in coordinates, one has to choose bases for the tangent spaces, resulting in a Jacobian matrix.

@@

\begin{table}
    \centering
    \caption{Group actions types available in \texttt{LieGroups.jl}.}
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Action type} & comment/code\\
        \midrule
        \verb|AdditionGroupAction| & falls back to \verb|+|\\
        \verb|ColumnwiseGroupAction{A}| & of a group action type \verb|A|\\
        \verb|(Inverse)LeftGroupOperationAction| & requires $\mathcal M = \mathcal G$\\
        \verb|LeftMultiplicationAction| & falls back to \verb|*|\\
        \verb|(Inverse)RightGroupOperationAction| & requires $\mathcal M = \mathcal G$\\
        \verb|RotationAroundAxisAction| & \\
        \verb|RowwiseGroupAction{A}| & of a group action type \verb|A|\\
        \bottomrule
    \end{tabular}
    \label{tab:GroupActionTypes}
\end{table}

Table~\ref{tab:GroupActionTypes} summarizes the currently implemented group action types in \verb|LieGroups.jl|.

\verb|apply|,
\verb|diff_apply|
\verb|diff_group_apply|
\verb|inv(A::GroupAction)|

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.15\textwidth]{logo.png}
    \caption*{\ \\[-.5\baselineskip]Logo of \texttt{LieGroups.jl}.}%
    \label{fig:liegroups_logo}
\end{figure}

@@

\subsection{Lie groups}
We denote a Lie group by \(\mathcal{G} = (\mathcal{M}, \cdot)\) where \(\mathcal{M}\) is a smooth manifold and \(\cdot\) is the group operation.
A smooth manifold \(\mathcal{M}\) is a topological space that is locally isomorphic to an Euclidean space \(\mathbb{R}^n\) for some \(n \in \mathbb{N}\), but globally may have a different topology.
We call \(n\) the dimension of the manifold \(\mathcal{M}\), denoted by \(\dim(\mathcal{M}) = n\).
As an example, take the \(2\)-dimensional sphere
\begin{equation*}
\mathbb{S}^2 = \bigl\{ p \in \mathbb{R}^3 \bigm| \lVert p\rVert = 1\bigr\},
\end{equation*}

@@

\subsubsection*{Exponential and logarithm.}
An important tool to “move around” on the Lie group is the exponential map.\\
The (Lie group) exponential function \(\exp\colon \mathfrak{g} \to \mathcal{G}\) maps elements from the Lie algebra to the Lie group, and is formally defined \cite[Def.~9.2.2]{HilgertNeeb:2012} by evaluating the unique curve \(\gamma\colon \mathbb{R} \to \mathcal{G}\) that fulfils the differential equation
\begin{equation*}
\gamma'(t) = D\lambda_{\gamma(t)}(e)[X]
\quad\text{ with }\quad\gamma(0) = e \text{ and }\gamma'(0) = X
\end{equation*}
at time $t=1$, i.e.\ \(\exp(X) = \gamma(1)\).

@@

The inner product and norm on the Lie algebra are available as \verb|inner(|$\frak g$\verb|, X, Y)| and \verb|norm(|$\frak g$\verb|, X)|, respectively.
Furthermore, there are two functions to convert between a coordinate-free representation of $X$ as a tangent vector and its representation in coordinates of a basis.

Given a vector $c \in \mathbb R^n$, we obtain the tangent vector by calling \verb|get_vector(|$\frak g$\verb|, c, b)| where \verb|b| is a basis of the tangent space, i.e.\ a subtype of \verb|AbstractBasis| and defaults within \verb|LieGroups.jl| to \verb|DefaultLieAlgebraOrthogonalBasis()|.
When a Lie group has different representations of points and tangent vectors, these are distinguished by calling \verb|get_vector(|$\frak g$\verb|, c, b, T)| specifying the tangent vector type.\footnote{in-place variant \texttt{get\_vector!($\frak g$, X::T, c, b)} contains the type information directly.}
Given a tangent vector $X \in \frak g$, we obtain its coordinates by calling \verb|get_coordinates(|$\frak g$\verb|, X, B)|\footnote{in-place variant \texttt{get\_coordinates!($\frak g$, c, X, b)}}, where the Basis is again optional.

@@

\subsubsection*{Jacobians}
On Euclidean space, the terms differential and Jacobian are often used interchangeably. Within differential geometry, the differential (or push forward) of a smooth map $f\colon \mathcal M \to \mathcal N$ between two manifolds is a map between the corresponding tangent spaces. We denote it by $Df(p)\colon T_p\mathcal M \to T_{f(p)}\mathcal N$, where $p \in \mathcal M$.
The differential is a linear map between the tangent spaces.
However, in the coordinate-free representation of tangent vectors, there is no matrix representation of this linear map.
But as soon as we choose bases for the tangent spaces and we represent tangent vectors in coordinates (cf.~\verb|get_coordinates| previously), we can represent the differential as a matrix, called the Jacobian matrix.

Currently for both \verb|exp| as well as \verb|conjugate|, the Jacobian is implemented. Note that for \verb|exp|, the domain is the Lie algebra. Since that is a vector space, its tangent space(s) can be identified with the Lie algebra again. Hence both Jacobians are maps from the Lie algebra to itself. The signatures are
\verb|jacobian_exp(G, p, X, b)|\footnote{in-place variant \texttt{jacobian\_exp!($\frak g$, J, p, X, b)}} and \verb|jacobian_conjugate(G, g, X, b)|\footnote{in-place variant \texttt{jacobian\_conjugate!($\frak g$, J, g, X, b)}}, where \verb|b| is again the basis to represent the tangent vectors in coordinates and defaults to \verb|DefaultLieAlgebraOrthogonalBasis()|.

@@

\begin{table}
    \centering
    \caption{Group actions types available in \texttt{LieGroups.jl}.}
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Group action type} & comment/code\\
        \midrule
        \verb|AdditionGroupAction| & falls back to \verb|+|\\
        \verb|ColumnwiseGroupAction{A}| & of a group action type \verb|A|\\
        \verb|(Inverse)LeftGroupOperationAction| & requires $\mathcal M = \mathcal G$\\
        \verb|LeftMultiplicationAction| & falls back to \verb|*|\\
        \verb|(Inverse)RightGroupOperationAction| & requires $\mathcal M = \mathcal G$\\
        \verb|RotationAroundAxisAction| & \\
        \verb|RowwiseGroupAction{A}| & of a group action type \verb|A|\\
        \bottomrule
    \end{tabular}
    \label{tab:GroupActionTypes}
\end{table}

Group actions as defined in Subsection~\ref{subsec:GroupActions} are implemented as a struct \verb|GroupAction{G, M, A} <: AbstractGroupAction| containing the Lie group \verb|G <: AbstractLieGroup|, the manifold \verb|M|, and a group action tpe \verb|A| in order to distinguish possible different ways a group could act on a manifold.
Table~\ref{tab:GroupActionTypes} summarizes the currently available group action types in \verb|LieGroups.jl|.

the main functions then are \verb|apply(a::GroupAction, g, p)|%
\footnote{in-place variant \texttt{apply!(a::GroupAction, q, g, p)}.}
to compute \(\sigma(g, p)\) for a group action \verb|a|, where $g\in \mathcal G$ and $p \in \mathcal M$, as well as its differential \verb|diff_apply(a::GroupAction, g, p, X)|%
\footnote{in-place variant \texttt{diff\_apply!(a::GroupAction, Y, g, p, X)}.}
to compute \(D\sigma(g, p)[X]\) for a tangent vector \(X \in T_p\mathcal M\) with respect to the manifold argument as well as \verb|diff_group_apply(a::GroupAction, g, p, Y)|%
\footnote{in-place variant \texttt{diff\_group\_apply!(a::GroupAction, Z, g, p, Y)}.}
to compute \(D\sigma(g, p)[Y]\) for a Lie algebra element \(Y \in \frak g\).

Due to the property that \(\sigma(g^{-1}, \sigma(g, p)) = p\) for all \(g \in \mathcal{G}\) and \(p \in \mathcal{M}\), there is also an inverse group action available $\sigma^{-1}(g, p) = \sigma(g^{-1}, p)$, which can be obtained by calling \verb|inv(a)|.

{\color{red} TODO: Discuss left and right group actions here?}

@@

For the \verb|CircleGroup()|, three different representations of points are available: as angles in \([0, 2\pi)\), as complex numbers with unit norm, and as points on the unit circle in \(\mathbb{R}^2\).
These are constructed by specifying the representation of points, i.e. \verb|CircleGroup(|$\mathbb R$\verb|)|, \verb|CircleGroup(|$\mathbb C$\verb|)|, and \verb|CircleGroup(|$\mathbb R^2$\verb|)|, respectively. Note that each of these representations uses a different underlying manifold, namely \verb|Circle(|$\mathbb R$\verb|)|, \verb|Circle(|$\mathbb C$\verb|)|, and \verb|Circle(|$\mathbb R^2$\verb|)|, respectively.
This is a case, where it is not only the representation of points and tangent vectors that differ, but indeed even the underlying manifold.
